Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-04-24 paper.tex
Minor fixes

Another function closely related to the three-point correlation function is the
cluster function which can be defined as:
\begin{equation}
  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle I_n^k(x) I_n^k(x + x_1) I_n^k(x + x_2) \rangle
\end{equation}
where $I_n^k$ is an indicator function for $k$-th cluster of $A_n$ and $K$
is a total number of clusters. A cluster is a subset of $A_n$ so that any two
points in this subset can be connected with a curve belonging to that subset.

By introducing a function $M_n(x) = |\nabla I_n(x)|$ which is a so-called interface
indicator function, we can define three additional
correlation functions -- these are the surface-surface-surface function
($F_{sss}$), surface-surface-void function ($F_{ssv}$) and surface-void-void
function ($F_{svv}$). They are defined as:
\begin{align}
  F_{sss}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) M_n(x + x_2) \rangle \\
  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle \\
  F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle
\end{align}
Here $I_{(void)}$ is an indicator function for the subset of the void phase
$A_v$. Unlike $S_3$ and $C_3$ functions, these functions do not have the meaning
of probability and have the units of measurement inversely proportional to
volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$,
$\mu m^{-2}$ and $\mu m^{-1}$ or other convenient dimensionless units depending
on the problem to be solved).  These functions describe the interface of the
subset $A_n$ and its spatial configuration with respect to $A_v$.

@@

To compute $C_3$ function we need to use a connected-component labeling
algorithm \cite{4728561,PhysRevB.14.3438} to label clusters. Then, again, a
slightly modified algorithm for $S_3$ is used to assess cluster function:
\begin{algorithmic}[1]
  \Procedure{$C_3$}{$A, n, x_1, x_2$}
  \State $A_n \gets I_n (A)$
  \State $C_n \gets \mathfrak{C}(A_n)$
  \State $C'_n \gets \mathfrak{S}_{x_1}(C_n)$
  \State $C''_n \gets \mathfrak{S}_{x_2}(C_n)$
  \State $Tmp \gets C_n \odot C'_n \odot C''_n$
  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
  \EndProcedure
\end{algorithmic}
Here $\mathfrak{C}$ is connected-component labeling operator and $\odot$ is
defined as follows:
\begin{equation}
  x \odot y = \left\{
  \begin{array}{ll}
    1 & \quad x = y \\
    0 & \quad \text{otherwise}.
  \end{array}
  \right.
\end{equation}

@@

On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
$\lambda=5000$ within a cube $[0, 1]^3$. Because $R \ll 1$, we can use
\cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
\cref{fig:balls-s3-comparison}.
\begin{figure*}[tp]
  \centering
  \subfigure[Realization of overlapping balls]{
    \includegraphics[width=0.4\linewidth]{images/balls.png}
    \label{fig:balls}}
  \hfill
  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and theoretical
    formula.]{
    \includegraphics[width=0.4\linewidth]{images/balls-s3.png}
    \label{fig:balls-s3-comparison}}
  \caption[]{A comparison of calculated and theoretical values of $S_3$ function
    for overlapping balls.}
  \label{fig:s3-verification}
\end{figure*}

>>>>

Another function closely related to the three-point correlation function is the
cluster function which can be defined as:
\begin{equation}
  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle I_n^k(x) I_n^k(x + x_1) I_n^k(x + x_2) \rangle
\end{equation}
where $I_n^k$ is an indicator function for $k$-th cluster of $A_n$ and $K$
is a total number of clusters. A cluster is a subset of $A_n$ such that any two
points in this subset can be connected with a curve belonging to that subset.

By introducing a function $M_n(x) = |\nabla I_n(x)|$ which is a so-called interface
indicator function, we can define three additional
correlation functions -- these are the surface-surface-surface function
($F_{sss}$), surface-surface-void function ($F_{ssv}$) and surface-void-void
function ($F_{svv}$). They are defined as:
\begin{align}
  F_{sss}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) M_n(x + x_2) \rangle \\
  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) I_{(void)}(x + x_2) \rangle \\
  F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle
\end{align}
Here $I_{(void)}$ is an indicator function for the subset of the void phase
$A_v$. Unlike $S_3$ and $C_3$ functions, these functions do not have the meaning
of probability and have the units of measurement inversely proportional to
volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$,
$\mu m^{-2}$ and $\mu m^{-1}$ or other convenient units depending on the problem
to be solved).  These functions describe the interface of the subset $A_n$ and
its spatial configuration with respect to $A_{(void)}$.

@@

To compute $C_3$ function we need to use a connected-component labeling
algorithm \cite{4728561,PhysRevB.14.3438} to label clusters. Then, again, a
slightly modified algorithm for $S_3$ is used to assess cluster function:
\begin{algorithmic}[1]
  \Procedure{$C_3$}{$A, n, x_1, x_2$}
  \State $A_n \gets I_n (A)$
  \State $C_n \gets \mathfrak{C}(A_n)$
  \State $C'_n \gets \mathfrak{S}_{x_1}(C_n)$
  \State $C''_n \gets \mathfrak{S}_{x_2}(C_n)$
  \State $Tmp \gets C_n \odot C'_n \odot C''_n$
  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
  \EndProcedure
\end{algorithmic}
Here $\mathfrak{C}$ is connected-component labeling operator and $\odot$ is
defined as follows:
\begin{equation}
  x \odot y = \left\{
  \begin{array}{ll}
    1 & \quad x = y \ne L_{(void)} \\
    0 & \quad \text{otherwise}.
  \end{array}
  \right.
\end{equation}
where $L_{(void)}$ is a label of the void phase.

@@

On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
$\lambda=5000$ within a cube $[0, 1]^3$. Because $R \ll 1$, we can use
\cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
\cref{fig:balls-s3-comparison}.
\begin{figure*}[tp]
  \centering
  \subfigure[Realization of overlapping balls]{
    \includegraphics[width=0.4\linewidth]{images/balls.png}
    \label{fig:balls}}
  \hfill
  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and a theoretical
    formula.]{
    \includegraphics[width=0.4\linewidth]{images/balls-s3.png}
    \label{fig:balls-s3-comparison}}
  \caption[]{A comparison of calculated and theoretical values of $S_3$ function
    for overlapping balls.}
  \label{fig:s3-verification}
\end{figure*}
